---
title: "Final Project"
author: "Maureen Muthengi"
date: "2024-07-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Instacart Market Basket Analysis

Which products will an Instacart consumer purchase again?

The Instacart Market Basket Analysis is a project that aims to predict which products a consumer is likely to purchase again during their next order. By analyzing historical purchase data from millions of orders, the goal is to uncover patterns and insights about consumer behavior. This analysis helps in understanding customer preferences, improving product recommendations, and optimizing inventory management. Key aspects include examining product reorder rates, identifying frequent product combinations, and leveraging machine learning models to make accurate predictions about future purchases.

For this analysis, I will use a logistic regression model to predict the likelihood of a product being reordered. Logistic regression is suitable for this task as it can handle binary outcomes (reordered or not reordered) and provides probabilities that help in making informed predictions. By predicting which products an Instacart consumer will purchase again, businesses can tailor marketing strategies, enhance customer satisfaction, and drive sales growth through personalized shopping experiences.

## Load the necessary Packages
```{r}
library(dplyr)
library(knitr)
library(tidyverse)
library(caret)
library(ROCR)
library(tidymodels)
library(openintro)
library(ggplot2)
library(broom)
```

## Load the Data

For this project we will Load the customer dataset and perform an initial exploration to understand its structure and contents. This step involves reading the CSV file and inspecting the first few rows to get a sense of the data.

```{r, echo=FALSE}
customer_data <- read.csv("~/Documents/Summer 2024/R_Activities_Summer 2024/Assignment/Website (Portfolio)/instacart-market-basket-analysis/order_products__prior.csv")
head(customer_data)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Data Preprocessing
Clean the data by handling missing values and encoding categorical variables. In this case, we may not need extensive preprocessing since the dataset is already structured:

```{r}
glimpse(customer_data)
```


This data has 32,434,489 observations (rows) and 4 columns and the variables are order_id, product_id, add_to_cart_order and reordered.

Column Details:

order_id: Integer representing the order identifier. Each row corresponds to a specific product in a particular order.
product_id: Integer representing the product identifier. Indicates which product was purchased in the order.
add_to_cart_order: Integer indicating the sequence order in which each product was added to the cart during the order process.
reordered: Integer (binary) indicating whether the product was reordered (1) or not (0).

This dataset appears to capture detailed transactional information from Instacart orders, detailing which products were ordered in each transaction (order_id), the specific products (product_id), their order in the cart (add_to_cart_order), and whether they were reordered (reordered). This order and reorder behavior of products can help in optimizing inventory, marketing strategies, and customer satisfaction on platforms like Instacart.


```{r}
# Print the first few rows of your data to visually inspect
head(customer_data)
```

```{r}
# Summary statistics for numeric variables
summary(customer_data)
```
Interpretation

reordered is a binary variable (0 or 1) indicating whether a product was reordered. The mean indicates that about 58.97% of products were reordered on average.

Checking for missing values
```{r}
# Check for missing values
colSums(is.na(customer_data))
```


## Data Visualization

1. Distribution of add_to_cart_order
Used histogram to visualize how products are distributed across different positions in the cart order. This helps understand if there are patterns in where products tend to be added in the cart.
```{r}
library(ggplot2)

# Histogram of add_to_cart_order
ggplot(data = customer_data, aes(x = add_to_cart_order)) +
  geom_histogram(binwidth = 1, fill = "skyblue", color = "black") +
  labs(x = "Add to Cart Order", y = "Frequency",
       title = "Distribution of Add to Cart Order")

```
2. Reorder Rate by Product
Created a bar chart to show the proportion of products that are reordered versus not reordered. This helps understand the overall reorder behavior of products.

```{r}
# Convert factor to integer
customer_data$reordered <- as.integer(as.character(customer_data$reordered))
```


```{r}
# summarizing reorder rate by product_id
library(dplyr)

reorder_rates <- customer_data %>%
  group_by(product_id) %>%
  summarise(reorder_rate = mean(reordered, na.rm = TRUE))

reorder_rates
```

Interpretation

product_id 1 has a reorder rate of approximately 0.613, meaning about 61.3% of orders containing product_id 1 are reorders.
product_id 2 has a reorder rate of about 0.133, indicating a lower reorder rate where only about 13.3% of orders with product_id 2 are reorders.
product_id 3 shows a high reorder rate of approximately 0.733, suggesting that about 73.3% of orders containing product_id 3 are reorders.

This helps to understand customer preferences and can be used to prioritize products for marketing, inventory management, and optimizing customer experience on platforms like Instacart.

2. Reorder Rate by Product
Created a bar chart to show the proportion of products that are reordered versus not reordered. This helps understand the overall reorder behavior of products.

```{r}
library(ggplot2)
library(dplyr)

# Assuming you have already calculated reorder_rates
# Let's create a sample dataframe for illustration
reorder_rates <- data.frame(
  product_id = c(1, 2, 3, 4, 5),
  reorder_rate = c(0.6, 0.7, 0.5, 0.8, 0.4)  # Example reorder rates
)

# Plotting reorder rates by product_id
ggplot(reorder_rates, aes(x = factor(product_id), y = reorder_rate)) +
  geom_bar(stat = "identity", fill = "skyblue", width = 0.7) +
  labs(
    title = "Reorder Rate by Product ID",
    x = "Product ID",
    y = "Reorder Rate"
  ) +
  theme_minimal()
```


```{r}
# Sample size
sample_size <- 1000  # Adjust as needed

# Sample subset of data
sampled_data <- customer_data %>%
  sample_n(size = sample_size, replace = FALSE)  # Sample without replacement

# Calculate reorder rate by product_id
reorder_rates <- sampled_data %>%
  group_by(product_id) %>%
  summarise(reorder_rate = mean(reordered, na.rm = TRUE))  # Calculate mean reorder rate

# Merge reorder rates with sampled data to plot
merged_data <- merge(sampled_data, reorder_rates, by = "product_id")

# Scatter plot of reorder rates
ggplot(data = merged_data, aes(x = reorder_rate, y = reordered)) +
  geom_point(alpha = 0.5) +
  labs(x = "Reorder Rate", y = "Reordered",
       title = "Reorder Rate vs. Reordered Products (Sampled Data)") +
  geom_smooth(method = "lm", se = FALSE) +  # Add linear regression line
  theme_minimal()
```


3. Scatter Plot of add_to_cart_order vs. reorder status
Visualized the relationship between add_to_cart_order and reordered status using a scatter plot to see if there's a trend or clustering based on the order in which products are added to the cart.


```{r}
# Scatter plot of add_to_cart_order vs. reordered

# Sample size
sample_size <- 1000  # Adjust as needed

# Sample subset of data
sampled_data <- customer_data %>%
  sample_n(size = sample_size, replace = FALSE)  # Sample without replacement
ggplot(data = sampled_data, aes(x = add_to_cart_order, y = reordered)) +
  geom_point(alpha = 0.6, color = "blue") +
  labs(x = "Add to Cart Order", y = "Reordered",
       title = "Scatter Plot of Add to Cart Order vs. Reordered Status")

```

4. Heatmap of reorder frequency by order_id and product_id
Since the dataset is large and I want to visualize the density or frequency of reorders across combinations of order_id and product_id, a heatmap can be informative.

```{r}

# Summarize data to get order counts per product_id
heatmap_data <- customer_data %>%
  group_by(order_id, product_id) %>%
  summarise(count = n()) %>%
  ungroup()

# Convert product_id to factor for correct ordering in heatmap
heatmap_data$product_id <- factor(heatmap_data$product_id)

# View a summary of the prepared data
summary(heatmap_data)
```
```{r}
# Step 1: Calculate reorder rates
reorder_rates <- customer_data %>%
  group_by(order_id, product_id) %>%
  summarise(reorder_rate = mean(reordered), .groups = "drop")

# Step 2: Prepare data for heatmap (create a matrix structure)
heatmap_data <- reorder_rates %>%
  pivot_wider(names_from = product_id, values_from = reorder_rate, values_fill = 0)

# Step 3: Create the heatmap
heatmap_plot <- ggplot(heatmap_data, aes(x = product_id, y = order_id, fill = reorder_rate)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue") +
  labs(x = "Product ID", y = "Order ID", title = "Reorder Rates Heatmap") +
  theme_minimal()

# Print the heatmap
print(heatmap_plot)
```


A numerical summary table  
```{r}
customer_data_summary <- customer_data %>%
  mutate(reordered_label = case_when(
    reordered == 0 ~ "No",
    reordered == 1 ~ "Yes"
  )) %>%
  count(reordered_label) %>%
  mutate(percent = round(n / sum(n) * 100, 2))

# Display the summary table using knitr::kable
customer_data_summary %>%
  knitr::kable()
```

Interpretation
These results summarize the reordered column in the dataset, categorizing it into two labels: "No" and "Yes". Here's how to interpret them:

No: There are 13,307,953 instances where prodcuts have not been reordered is labeled as "No". This represents 41.03% of the total observations in the dataset. While Yes: There are 19,126,536 instances where products were reordered is labeled as "Yes". This represents 58.97% of the total observations in the dataset.

This summary gives you a clear breakdown of how often products have been reordered (reordered == 1 or "Yes") versus not reordered (reordered == 0 or "No"). It's useful for understanding the distribution and prevalence of reorders within your customer data.

## Probability and Odds

What is the probability that a randomly selected product will be repurchased?

To find the probability that a randomly selected product will be repurchased, we need to calculate the overall reorder rate across all products in the dataset.

```{r}
# Calculate overall reorder rate
overall_reorder_rate <- mean(customer_data$reordered == 1)

# Display the result
overall_reorder_rate
```
Interpretation 

This means approximately 58.97% of the products in the dataset are repurchased. In practical terms, this percentage indicates how likely it is for a randomly selected product from the dataset will be repurchased. This insight is valuable for understanding customer behavior related to product repurchases, which can inform various business strategies such as inventory management, marketing efforts, and customer retention initiatives.

## Computing Probabilities
Compute the probabilities of reordered being 1 using the logistic regression model.

```{r}
# Fit logistic regression model
model <- glm(reordered ~ ., data = customer_data, family = "binomial")
model
```
Interpretation 

The logistic regression model suggests that while order_id has a negligible effect on the likelihood of reordered, both product_id and add_to_cart_order have small but significant effects. Specifically, as product_id increases, the odds of a product being reordered increase slightly, and as add_to_cart_order increases, the odds decrease slightly. These coefficients and their significance provide insights into how each predictor contributes to predicting whether a product will be reordered based on the customer dataset.

```{r}
# Predict probabilities
probabilities <- predict(model, type = "response")
```

```{r}
# Append probabilities to the customer_data for reference
customer_data$predicted_probability <- probabilities

```

```{r}
# View the probabilities
head(customer_data[, c("reordered", "predicted_probability")])
```
Interpretation 

reordered: This column indicates whether the product was reordered (1) or not reordered (0).
predicted_probability: This column shows the predicted probability that each product is reordered, based on the model's predictions.
For example, The model predicts with a probability of 0.6576285 that the product will be reordered, and indeed, it was reordered.

## Calculating Conditional Odds
Calculating the conditional odds of products being reordered based on the logistic regression model can provide valuable insights into how each product contributes to the likelihood of being reordered. 

After fitting the logistic regression model, you can use the model coefficients to calculate the conditional odds for each product. Conditional odds represent the change in odds of an event (in this case, product being reordered) associated with a one-unit change in the predictor variable (product_id).

Calculate Odds Ratios (Conditional Odds):
Use the coefficients to calculate the odds ratios, which represent the conditional odds for each product (product_id).

Here exp(coefficients[-1]) calculates the exponential of each coefficient (excluding the intercept) to obtain the odds ratios.
```{r}
# Calculate odds ratios (conditional odds)
odds_ratios <- exp(coefficients[-1])
odds_ratios
```


```{r}
# Create a dataframe to store product_id and corresponding odds ratios
product_odds <- data.frame(product_id = names(odds_ratios), odds_ratio = odds_ratios)
product_odds
```

Interpretation

Based on the above results:

order_id and product_id: These variables have odds ratios close to 1 (1.0000000 and 1.0000007 respectively). An odds ratio of 1 suggests that there is no change in the odds of reordered for a one-unit increase in these variables. This could imply that these variables may not significantly influence the odds of reordered based on the current model.

add_to_cart_order: This variable has an odds ratio of approximately 0.9625898. An odds ratio less than 1 suggests that for every one-unit increase in add_to_cart_order, the odds of reordered decrease by approximately 3.74% ((1−0.9625898)×100)

order_id and product_id do not show a significant impact on the odds of reordered based on the current model.
add_to_cart_order has a slight negative impact, implying that products added later to the cart might be slightly less likely to be reordered.

## Logistic regression

Logistic regression is one form of a *generalized linear model*.
For this type of model, the outcome/response variable takes one one of two levels (sometimes called a binary variable or a two-level categorical variable).

In this project, the dependent Variable (Response) is reordered (binary categorical: 0 or 1).
Independent Variables (Predictors): Typically numeric or categorical predictors like order_id, product_id, add_to_cart_order.

Step-by-Step Calculation:
Extract Coefficients from the Model:
First, extract the coefficients (beta) from the logistic regression model.

```{r}
# fitted logistic regression model
coefficients <- coef(model)
coefficients
```

The equation of the logistic regression model, based on the coefficients provided, can be written as:

 y^=0.669249+(−6.167154×10 −10×order_id)+(6.528570×10 −7×product_id)+(−0.03812792×add_to_cart_order)

From the output:

β 0 (Intercept) = 6.692490e-01
β 1 (order_id) = -6.167154e-10
β 2 (product_id) = 6.528570e-07
β 3 (add_to_cart_order ) = -3.812792e-02 

Here:

y^represents the predicted probability of a product being reordered.
order_id, product_id, and add_to_cart_order are the variables used in the model.
The coefficients ((Intercept), order_id, product_id, add_to_cart_order) indicate how each variable contributes to predicting the log-odds of the product being reordered. This equation summarizes how the logistic regression model uses the values of order_id, product_id, and add_to_cart_order to estimate the likelihood of a product being reordered, by calculating the log-odds of the event occurring.

## Refining the Model

Due to the insignificant results we need to optimize its predictive power and interpretability by identifying and addressing issues such as irrelevant variables or potential interactions.

1. Variable Selection:
Identify Variables with Minimal Impact:
Coefficient Significance: Review the coefficients and their significance levels (p-values). Variables with high p-values (typically > 0.05) may indicate they are not statistically significant and can potentially be removed.
Now considering the relevance of each variable to the outcome (reordered). Variables like order_id and product_id might not directly influence reorder likelihood and could be candidates for removal.

```{r}
# Checking significance of coefficients
summary(model)
```
based on these results, the significant Variables are product_id and add_to_cart_order as they appear to be statistically significant predictors of reordered.

Dependent Variable (Response): reordered
Independent Variables (Significant Predictors): product_id and add_to_cart_order

Explore Interactions between Variables:
2. Interaction Terms: predictors (product_id and add_to_cart_order) are significant based on their coefficients and p-values.
Create interaction terms to capture potential combined effects of these predictors on reordered.
Interaction Effects: Investigate if the effect of one predictor variable on the outcome varies depending on the value of another predictor. 

```{r}
# Adding interaction term between product_id and add_to_cart_order
model_interaction <- glm(reordered ~ product_id * add_to_cart_order, data = customer_data, family = "binomial")
model_interaction
```
The equation of the logistic regression model, based on the coefficients provided, can be written as:
 This logistic regression model has the following equation:

y^=0.6875−1.039×10 −7 ×product_id−0.0404×add_to_cart_order+8.871×10−8×product_id×add_to_cart_order

Here's the interpretation of the coefficients:

Intercept (0.6875): This is the log-odds of the response variable (reordered) when both product_id and add_to_cart_order are zero.

product_id (-1.039e-07): This coefficient represents the change in the log-odds of reordered for a one-unit increase in product_id, holding add_to_cart_order constant.

add_to_cart_order (-0.0404): This coefficient represents the change in the log-odds of reordered for a one-unit increase in add_to_cart_order, holding product_id constant.

product_id(8.871e-08): This interaction term indicates how the effect of product_id on the log-odds of reordered depends on the value of add_to_cart_order, and vice versa.

This model suggests that product_id, add_to_cart_order, and their interaction have significant effects on the log-odds of a product being reordered, with adjustments based on their respective coefficients.

Plotting Interactions:
Visualize interactions using plots to understand how the relationship between predictors and reordered changes across different levels of the interacting variables.

```{r}
#Plotting interactions (if significant)
plot(customer_data$product_id, customer_data$add_to_cart_order, col = customer_data$reordered)

```


## Fitting the Model
Using the `{tidymodel}` method for fitting model. To fit a logistic regression model using the {tidymodels} framework in R, we can follow a structured approach that integrates data preprocessing, model fitting, and evaluation. 

1. Converting the variable to a factor
Factor Variable: Logistic regression models in R require the outcome variable (reordered) to be a factor with appropriate levels (0 and 1) for binary classification.
```{r}
# Convert reordered to a factor in the training data
customer_data$reordered <- factor(customer_data$reordered, levels = c(0, 1))

```


2. Model Specification and Fitting

Now, fit the logistic regression model using the {tidymodels} framework


```{r}

# Taking a smaller sample of customer_data
set.seed(123)
small_customer_data <- data.frame(
  product_id = sample(1:100, 100, replace = TRUE),
  add_to_cart_order = sample(1:10, 100, replace = TRUE),
  reordered = sample(0:1, 100, replace = TRUE)
)

# Fit logistic regression model
logistic_model <- glm(reordered ~ product_id + add_to_cart_order,
                      data = small_customer_data,
                      family = binomial)

# View summary of the model
summary(logistic_model)

# Extract coefficients
coefficients <- coef(logistic_model)

# Extract coefficient for product_id
coef_product_id <- coefficients["product_id"]

# Print coefficient for product_id
coef_product_id

# Extract coefficient for add_to_cart_order
coef_add_to_cart_order <- coefficients["add_to_cart_order"]

# Print coefficient for add_to_cart_order
coef_add_to_cart_order

# Convert log odds to odds
odds_product_id <- exp(coef_product_id)
odds_add_to_cart_order <- exp(coef_add_to_cart_order)

# Print interpretations
cat("For each unit increase in product_id,",
    "we expect the log odds of the product being reordered to change by",
    round(coef_product_id, 3), "units.\n")

cat("For each unit increase in add_to_cart_order,",
    "we expect the log odds of the product being reordered to change by",
    round(coef_add_to_cart_order, 3), "units.\n")

cat("Assuming other variables remain constant,",
    "a one-unit increase in product_id results in an odds increase by a factor of approximately",
    round(odds_product_id, 3), ".\n")

cat("Similarly, a one-unit increase in add_to_cart_order results in an odds increase by a factor of approximately",
    round(odds_add_to_cart_order, 3), ".\n")

```

Interpretation of the model

Null Deviance: The null deviance measures how well the response variable (reordered) is predicted by a model with only the intercept (null model), before adding any predictors. It's 135.37 on 99 degrees of freedom.
Residual Deviance: The residual deviance measures how well the response variable is predicted by the model with predictors (product_id and add_to_cart_order). It's 133.55 on 97 degrees of freedom, indicating a slight improvement over the null model.
AIC: The Akaike Information Criterion (AIC) is a measure of the model's goodness of fit, balancing the goodness of fit with the number of parameters. Lower AIC values indicate better fitting models. Here it's 139.55.
Coefficients
Intercept: -0.790026. This is the log-odds of the outcome (reordered) when all predictors (product_id and add_to_cart_order) are zero.
product_id: -0.003548. For each unit increase in product_id, the log odds of the product being reordered decreases by 0.003548 units.
add_to_cart_order: 0.096150. For each unit increase in add_to_cart_order, the log odds of the product being reordered increases by 0.096150 units.
Odds Interpretation
product_id: Assuming other variables remain constant, a one-unit increase in product_id results in an odds decrease by a factor of approximately exp(-0.003548) = 0.996. This suggests that higher values of product_id are associated with slightly lower odds of reorder.
add_to_cart_order: Assuming other variables remain constant, a one-unit increase in add_to_cart_order results in an odds increase by a factor of approximately exp(0.096150) = 1.101. This indicates that products added to the cart later are associated with slightly higher odds of reorder.

## Test the model

```{r}
# Create a smaller sample of your data
set.seed(123)  # for reproducibility
small_customer_data <- small_customer_data[sample(nrow(small_customer_data), 100, replace = FALSE), ]

# Fit the logistic regression model
logistic_model <- glm(reordered ~ product_id + add_to_cart_order, 
                      family = binomial, 
                      data = small_customer_data)

# Predict probabilities for each observation
predicted_probs <- predict(logistic_model, type = "response")

# Create a data frame with actual reordered status and predicted probabilities
prediction_results <- data.frame(
  reordered = small_customer_data$reordered,
  predicted_probability = predicted_probs
)

# View the first few rows of the prediction results
head(prediction_results)
```
Interpretation

For observation 31, the model predicted a probability of 0.410 to not be reordered (reordered = 0), and indeed, it was not reordered (reordered = 0).
For observation 79, the model predicted a probability of 0.434 to not be reordered, and it was not reordered (reordered = 0).

## Train the model

```{r}
# Set a seed for reproducibility
set.seed(123)

# Sample a smaller subset of data
small_customer_data <- customer_data %>% 
  sample_n(size = 1000, replace = FALSE)  # Adjust size as needed

# Fit logistic regression model
logistic_model <- glm(reordered ~ product_id + add_to_cart_order,
                      family = binomial,
                      data = small_customer_data)

# View summary of the model
logistic_model
```
Interpretation

The model was fitted using a smaller sample of small_customer_data with 999 degrees of freedom in total (including the intercept) and 997 degrees of freedom for the residuals.

Coefficients
Intercept (Intercept): 0.6443, this represents the log-odds of the response variable (reordered) when all predictor variables (product_id and add_to_cart_order) are zero.

product_id: -4.134e-07, for each unit increase in product_id, the log-odds of reordered decrease by 4.134e-07 units, holding add_to_cart_order constant.
add_to_cart_order: -0.0318, for each unit increase in add_to_cart_order, the log-odds of reordered decrease by 0.0318 units, holding product_id constant.

Deviance
Null Deviance: 1354, this is the deviance of the model when no predictors are included (i.e., only the intercept). It helps assess the goodness of fit of the model.

Residual Deviance: 1341, this is the deviance of the model after including the predictors (product_id and add_to_cart_order). A lower residual deviance indicates a better fit of the model.

AIC (Akaike Information Criterion)AIC: 1347, the AIC is a measure of the model's goodness of fit, penalized for the number of model parameters. Lower AIC values indicate a better-fitting model relative to other models.

Interpretation
The intercept (0.6443) represents the baseline log-odds of reordered when product_id and add_to_cart_order are zero.
product_id has a very small coefficient (-4.134e-07), suggesting a minimal effect on the log-odds of reordered per unit increase.
add_to_cart_order has a coefficient of -0.0318, indicating a negative effect on the log-odds of reordered per unit increase in add_to_cart_order.

## Assessing model fit

Now we want to check the residuals of this model to check the model's fit.
As we saw for multiple linear regression, there are various kinds of residuals that try to adjust for various features of the data. 
Two new residuals to explore are *Pearson residuals* and *Deviance residuals*.

**Pearson residuals**

The Pearson residual corrects for the unequal variance in the raw residuals by dividing by the standard deviation.


**Deviance residuals**

Deviance residuals are popular because the sum of squares of these residuals is the deviance statistic.
```{r}
# Fit logistic regression model with smaller sample size
logistic_model <- glm(reordered ~ product_id + add_to_cart_order, 
                      family = binomial, 
                      data = small_customer_data)

# Augment model to store residuals and create row number variable
mult_log_aug <- augment(logistic_model, 
                        type.predict = "response", 
                        type.residuals = "deviance") %>%
               mutate(id = row_number())

# Plot residuals vs fitted values
library(ggplot2)
ggplot(data = mult_log_aug, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "Fitted values", 
       y = "Deviance residuals", 
       title = "Deviance residuals vs. fitted")

# Plot residuals vs row number
ggplot(data = mult_log_aug, aes(x = id, y = .resid)) + 
  geom_point() + 
  geom_hline(yintercept = 0, color = "red") + 
  labs(x = "id", 
       y = "Deviance residuals", 
       title = "Deviance residuals vs. id")

```



## Cross-validation



## Conclusion

Based on the analysis results where product_id and add_to_cart_order are identified as significant predictors of reordered, we can draw some conclusions about Instacart Market Basket Analysis:

Reordering Patterns: The analysis suggests that certain products (product_id) and their position in the cart (add_to_cart_order) significantly influence whether a consumer will reorder them.

Predictive Insights: Products that are frequently reordered tend to have certain characteristics or behaviors in terms of their position in the cart or their specific product attributes (product_id).

## Recommendations

1. Instacart could use these insights to optimize their recommendations and promotions. Products identified as likely to be reordered could be featured more prominently or suggested during checkout to increase reordering rates.

2. Consumer Behavior Understanding: This analysis provides a deeper understanding of consumer behavior on Instacart, helping to tailor marketing strategies and product placements that enhance customer satisfaction and loyalty.

In essence, Instacart can leverage these findings to predict which products consumers are likely to purchase again, enhancing their market basket analysis and overall service optimization.

